Price of Anarchy for Mean Field Games

### 2018-08-02 PoA.tex
moved h_u, h_w definitions earlier in Prop 4

% proposition b_2 to \infty
\begin{proposition}
	Assume Assumption \ref{assumption}. If:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then:
	$$ \lim_{b_2 \to \infty} PoA = 1.$$
	Otherwise,
	$$ \lim_{b_2 \to \infty} PoA > 1.$$
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}},
	\end{equation*}
	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{equation*}
	\begin{split}
		(b_2 + \bar{b}_2) u^{b_2}_t &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		\\
		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{split}
	\end{equation*}
	Similarly, for all $t \in [0,T)$:
	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
	$$ 
	and thus for all $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}
	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$ and all $t\in[0,T]$:
	\begin{equation}
	   b_2 \eta_t^{b_2} \geq m_\eta.
	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
	\end{equation}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Case 1: c_u = c_w
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%		
	\textbf{Case 1:} Assume:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}.
	\end{equation*}
	Then $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	with:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% case 2: c_u \neq c_w
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\textbf{Case 2:} Assume:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}.
	\end{equation*}
	Then $c_u \neq c_w$. We want to show that $\lim_{b_2 \to \infty}PoA^{b_2}>1$. To do so, we will show that $(b_2 + \bar{b_2}) \Delta SC^{b_2}\geq c_{num}>0$ and $b_2 SC^{MKV,b_2} \leq M_{den}<\infty$ for large $b_2$, where $c_{num}$ and $M_{den}$ are two constants independent of $b_2$. We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$, as defined prior to Case 1. Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions. Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.

@@

	Next, consider the quantity $J^{b_2}_2$, which can be written as:
	\begin{IEEEeqnarray*}{rCl}
		J^{b_2}_2 &=& \frac{1}{2 (r + \bar{r}) }\int_0^T \left(b_2 \eta_t^{b_2} \right)^2 Var(\xi) e^{2b_1 t} \cdot b_2 \exp \left( - 2 B^{\eta,b_2} \int_0^t \eta_s ds \right) dt \nonumber \\
		&& \hspace{10em}  + \frac{\sigma^2}{2} \cdot  b_2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \left( \int_0^t e^{2b_1(t-s) - 2B^{\eta,b_2} \int_s^t \eta_u^{b_2} du} ds \right)  dt .
	\end{IEEEeqnarray*}
	We will make use of Lemma \ref{lemma:int_b2_eta_t}, which appears below, and states that there exists $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$: 
	\begin{equation}
	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{l}.
	\label{eq:intgeral_b2_eta_t_bound_b2_infinity}
	\end{equation}

	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
	Thus, together with inequalities (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}), and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_6 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
	\begin{IEEEeqnarray}{rCl}
		J^{b_2}_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta^{b_2}_t \right)^2 b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 b_2^3  e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{l} \nonumber \\
		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{l}}{2} =: M_{J_2}.
	\label{eq:J2_upper_bound_b2_infinity}
	\end{IEEEeqnarray} 
	Now, from equation (\ref{eq:J1_plus_J2_b2_infinity}) and inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), we have for all $b_2 \geq b_2^{*,den} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
	\begin{equation} 
		b_2 SC^{MKV, b_2}  = J^{b_2}_1 + J^{b_2}_2 \leq M_{J_1} + M_{J_2} =: M_{den}.
	\label{eq:demumerator_ineq_b2_infinity}
	\end{equation}

>>>>

% proposition b_2 to \infty
\begin{proposition}
	Assume Assumption \ref{assumption}. If:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then:
	$$ \lim_{b_2 \to \infty} PoA = 1.$$
	Otherwise,
	$$ \lim_{b_2 \to \infty} PoA > 1.$$
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}},
	\end{equation*}
	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
	For the sake of simplicity, denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{equation*}
	\begin{split}
		h_u(b_2,t) &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		\\
		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{split}
	\end{equation*}
	Similarly, for all $t \in [0,T)$:
	$$\lim_{b_2 \to \infty} h_w(b_2,t)=  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
	$$ 
	and thus for all $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		h_u(b_2,t) &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}
	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$ and all $t\in[0,T]$:
	\begin{equation}
	   b_2 \eta_t^{b_2} \geq m_\eta.
	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
	\end{equation}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Case 1: c_u = c_w
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%		
	\textbf{Case 1:} Assume:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}.
	\end{equation*}
	Then $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$ and thus:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	with:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% case 2: c_u \neq c_w
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\textbf{Case 2:} Assume:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}.
	\end{equation*}
	Then $c_u \neq c_w$. We want to show that $\lim_{b_2 \to \infty}PoA^{b_2}>1$. To do so, we will show that $(b_2 + \bar{b_2}) \Delta SC^{b_2}\geq c_{num}>0$ and $b_2 SC^{MKV,b_2} \leq M_{den}<\infty$ for large $b_2$, where $c_{num}$ and $M_{den}$ are two constants independent of $b_2$. We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$, as defined prior to Case 1. Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions. Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $h_u(b_2,t) \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.

@@

	Next, consider the quantity $J^{b_2}_2$, which can be written as:
	\begin{IEEEeqnarray*}{rCl}
		J^{b_2}_2 &=& \frac{1}{2 (r + \bar{r}) }\int_0^T \left(b_2 \eta_t^{b_2} \right)^2 Var(\xi) e^{2b_1 t} \cdot b_2 \exp \left( - 2 B^{\eta,b_2} \int_0^t \eta_s ds \right) dt \nonumber \\
		&& \hspace{10em}  + \frac{\sigma^2}{2} \cdot  b_2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \left( \int_0^t e^{2b_1(t-s) - 2B^{\eta,b_2} \int_s^t \eta_u^{b_2} du} ds \right)  dt .
	\end{IEEEeqnarray*}
	We will make use of Lemma \ref{lemma:int_b2_eta_t}, which appears below, and states that there exists $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$: 
	\begin{equation}
	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{l}.
	\label{eq:intgeral_b2_eta_t_bound_b2_infinity}
	\end{equation}
	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
	Thus, together with inequalities (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}), and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_6 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
	\begin{IEEEeqnarray}{rCl}
		J^{b_2}_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta^{b_2}_t \right)^2 b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 b_2^3  e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{l} \nonumber \\
		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{l}}{2} =: M_{J_2}.
	\label{eq:J2_upper_bound_b2_infinity}
	\end{IEEEeqnarray} 
	Now, from equation (\ref{eq:J1_plus_J2_b2_infinity}) and inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), we have for all $b_2 \geq b_2^{*,den} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
	\begin{equation} 
		b_2 SC^{MKV, b_2}  = J^{b_2}_1 + J^{b_2}_2 \leq M_{J_1} + M_{J_2} =: M_{den}.
	\label{eq:demumerator_ineq_b2_infinity}
	\end{equation}
